Supermassive black holes and their host spheroids \\ III. The $M_{\rm BH} - \lowercase{n_{\rm sph}}$ correlation

### 2015-12-17 papers/mbhn/ApJ_Submission/mbhn.tex
thu

\shorttitle{A universal $M_{\rm BH} - n_{\rm sph}$ correlation}
\shortauthors{Savorgnan}

@@

\title{Supermassive black holes and their host spheroids \\ 
III. A universal $M_{\rm BH} - \lowercase{n_{\rm sph}}$ correlation }

@@

\begin{abstract}
The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution of stellar spheroidal and disk components, 
with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, has been shown to tightly correlate 
with the mass of the central supermassive black hole, $M_{\rm BH}$. 
The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known scaling relations 
involving the spheroid luminosity, $L_{\rm sph}$: 
the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$ correlations. 
Obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of a galaxy's light distribution 
and some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
and other black hole mass scaling relations, 
we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
In this paper, the third of its series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
they reunite into a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
with relatively small intrinsic scatter ($\epsilon_{(M_{\rm BH} | n_{\rm sph})} \simeq 0.25 \rm~dex$). 
The black hole mass is therefore closely related to the spheroid central concentration of stars, 
which mirrors the inner gradient of the spheroid gravitational potential. 
\end{abstract}

@@

of the light distribution of the stellar spheroidal\footnote{Throughout the text, we use the term ``spheroid'' to designate 
either a diskless elliptical galaxy or the bulge component of a disk galaxy, 
with no attempt at distinguishing between classical bulges and disk-like pseudo-bulges. } and disk components of galaxies 

@@

The S\'ersic model parametrizes the intensity of light $I$ as a function of the projected galactic radius $R$ such that

@@

but they unexpectedly failed to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation. 

@@

and showed that, by rejecting the most discrepant measurements and averaging the remaning ones, 

@@

Here we focus on the $M_{\rm BH} - n_{\rm sph}$ relation. \\
This paper (\emph{Paper III}) is structured as follows...

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample used in \emph{Paper II} (and presented here in Table \ref{tab:sample}), 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
\cite{ellicular} demonstrate that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices were estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by other studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes, which report only the statistical errors 
associated with their fitted parameters. 
Readers should refer to \emph{Paper I} for a more detailed discussion on this topic. }. 
For the present analysis, we elected to use the spheroid S\'ersic indices obtained from the decomposition of the one-dimensional 
major-axis surface brightness profiles of our galaxies.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes the two galaxies classified as E/S0, 
whereas the two galaxies classified as S0/Sp and the two galaxies classified as ``mergers'' are included in neither the early- nor the late-type bin.

@@

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001bulges}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{grahamworley2008} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{grahamworley2008} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
%It is also worth mentioning that, 
%although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
%{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram using only our high-quality dataset. 
Spheroid luminositites and S\'ersic indices were obtained from accurate multicomponent decompositions,  
performed in a consistent manner using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{grahamworley2008} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
According to the modified FITEXY routine, 
early-type galaxies\footnote{Using the BCES estimator, 
\cite{savorgnan2013} re-analyzed the dataset from \cite{grahamguzman2003} 
and obtained $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$ for the elliptical galaxies only. 
This result is in excellent agreement with the BCES linear regression obtained here for the early-type galaxies 
($L_{\rm sph} \propto n_{\rm sph}^{3.89 \pm 0.42}$) 
and, remarkably, it is exactly the same proportionality obtained here for the early-type galaxies with the modified FITEXY routine. } 
follow $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
whereas late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend).
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevented us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations. 
%($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
%and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we know that the early-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{1.03 \pm 0.11}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
therefore we expect to find $M_{\rm BH} \propto n_{\rm sph}^{3.69 \pm 0.44}$; 
this prediction is in excellent agreement with the observed log-slope of $3.58 \pm 0.27$ obtained here. 
On the other hand, late-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{2.58 \pm 1.06}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$, 
from which one can predict $M_{\rm BH} \propto n_{\rm sph}^{3.72 \pm 2.03}$; 
this is consistent with the observed log-slope of $4.55 \pm 0.66$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
In both cases, the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph} - 0.50 \bigr) . 
\end{equation*}
\\

We have seen that the early- and late-type galaxies in the $M_{\rm BH} - n_{\rm sph}$ diagram 
can be fit (together) with a single power-law, 
whereas they follow two different correlations in the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). 
We now want to compare the amount of intrinsic scatter in these two plots. 
In Table \ref{tab:intsc} we report the values of the intrinsic scatter 
in the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams 
for all, early- and late-type galaxies, 
obtained with the modified FITEXY routine and the Bayesian estimator {\tt linmix\_err}. 
When considering all galaxies, irrespective of their morphological type, 
the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation. 
However, this is obviously not a fair comparison, 
because of the different nature of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
(single and double power-law, respectively). 
One can obtain more informative results by considering early- and late-type galaxies separately. 
For the early-type galaxies, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent\footnote{Looking 
at the results obtained with the modified FITEXY routine, 
the values of the intrisic scatter are only marginally consistent with each other, 
but looking at the results obtained with the Bayesian estimator {\tt linmix\_err}, 
the values of the intrisic scatter are fully consistent with each other. } 
with that of the $M_{\rm BH} - L_{\rm sph}$ relation (within their $1\sigma$ uncertainties). 
For the late-type galaxies, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent with 
that of the $M_{\rm BH} - L_{\rm sph}$ relation, 
except for the inverse ($X|Y$) regression obtained with the modified FITEXY routine. \\
In passing, we note that the values of the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation 
are systematically smaller -- although consistent within the errors -- 
than the corresponding values of the intrinsic scatter of the $M_{\rm BH} - L_{\rm sph}$ relation.  
In addition, the values of the intrinsic scatter returned by the modified FITEXY routine are systematically smaller than 
those output by the Bayesian estimator {\tt linmix\_err}.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend). 
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:mbhn}
\end{center}
\end{figure}

>>>>

\shorttitle{The $M_{\rm BH} - n_{\rm sph}$ correlation}
\shortauthors{Savorgnan}

@@

\title{Supermassive black holes and their host spheroids \\ 
III. The $M_{\rm BH} - \lowercase{n_{\rm sph}}$ correlation }

@@

\begin{abstract}
The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution of stellar spheroidal and disk components, 
with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, has been shown to tightly correlate 
with the mass of the central supermassive black hole, $M_{\rm BH}$. 
The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known scaling relations 
involving the spheroid luminosity, $L_{\rm sph}$: 
the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$. 
Obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of a galaxy's light distribution 
and some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
and other black hole mass scaling relations, 
we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
In this paper, the third of this series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
they reunite into a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
with relatively small intrinsic scatter ($\epsilon_{(M_{\rm BH} | n_{\rm sph})} \simeq 0.25 \rm~dex$). 
The black hole mass appears to be closely related to the spheroid central concentration of stars, 
which mirrors the inner gradient of the spheroid gravitational potential. 
\end{abstract}

@@

of the light distribution of the stellar spheroidal\footnote{Throughout the text, we use the term ``spheroid'' to indicate 
either a disk-less elliptical galaxy or the bulge component of a disk galaxy;  
we do not attempt at distinguishing between classical bulges and disk-like pseudo-bulges. } and disk components of galaxies 

@@

The S\'ersic model parameterizes the intensity of light $I$ as a function of the projected galactic radius $R$ such that

@@

but they failed to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation. 

@@

and showed that, by rejecting the most discrepant measurements and averaging the remaining ones, 

@@

Here we focus on the $M_{\rm BH} - n_{\rm sph}$ relation.

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample used in \emph{Paper II} (and presented here in Table \ref{tab:sample}), 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to establish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
\cite{ellicular} demonstrate that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices were estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by other studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes, which report only the statistical errors 
associated with their fitted parameters. 
Readers should refer to \emph{Paper I} for a more detailed discussion on this topic. }. 
For the present analysis, we elected to use the spheroid S\'ersic indices obtained from the decomposition of the one-dimensional 
major-axis surface brightness profiles of our galaxies.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes the two galaxies classified as E/S0, 
whereas the two galaxies classified as S0/Sp and the two galaxies classified as ``mergers'' are included in neither the early- nor the late-type bin.

@@

\subsection{$L_{\rm sph} - n_{\rm sph}$}
Following \cite{graham2001bulges}, 
who showed that the $L_{\rm sph} - n_{\rm sph}$ relation is different for elliptical galaxies and the bulges of disk galaxies (S0+Sp), 
\cite{savorgnan2013} re-analyzed the data from \cite{grahamguzman2003} and \cite{grahamworley2008} 
and obtained two separate $L_{\rm sph} - n_{\rm sph}$ linear regressions for elliptical galaxies and the bulges of disk galaxies 
(in the B- and K-band, respectively). 
At the time, the $L_{\rm sph} - n_{\rm sph}$ datasets from \cite{grahamguzman2003} and \cite{grahamworley2008} were of the best quality available 
to investigate the $L_{\rm sph} - n_{\rm sph}$ relation for different galaxy morphological types. 
However, these datasets were not obtained from a homogeneous analysis, 
but they were a collection of results taken from various past bulge/disk decomposition studies. 
%It is also worth mentioning that, 
%although the K-band luminosities of the bulges of disk galaxies had been corrected for internal dust absorption, 
%{\bf such corrections are still not very accurate today?!? Driver et al. xxxx??? }  
Here we re-investigate the $L_{\rm sph} - n_{\rm sph}$ diagram using only our high-quality dataset. 
Our spheroid luminosities and S\'ersic indices were obtained from accurate multicomponent decompositions,  
performed in a consistent manner using the $3.6\rm~\mu m$ band, which is less affected by dust extinction than the K-band. \\
\cite{grahamworley2008} presented a single $L_{\rm sph} - n_{\rm sph}$ correlation for the bulges of disk galaxies (S0+Sp).
However, using our dataset, 
we fit the $L_{\rm sph} - n_{\rm sph}$ relation for elliptical, lenticular and spiral galaxies separately, 
and found that the values of the slope and intercept for the lenticular galaxies 
are not consistent within the errors with those for the spiral galaxies, 
but are consistent within the errors with those for the elliptical galaxies.  
Given this, we conclude that in the $L_{\rm sph} - n_{\rm sph}$ diagram 
elliptical and lenticular galaxies form together a single (\emph{early-type}) sequence, 
whereas the combination of lenticular and spiral galaxies do not. 
According to the modified FITEXY routine, 
early-type galaxies\footnote{Using the BCES estimator, 
\cite{savorgnan2013} re-analyzed the dataset from \cite{grahamguzman2003} 
and obtained $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$ for the elliptical galaxies only. 
This result is in excellent agreement with the BCES linear regression obtained here for the early-type galaxies 
($L_{\rm sph} \propto n_{\rm sph}^{3.89 \pm 0.42}$) 
and, remarkably, it is exactly the same proportionality obtained here for the early-type galaxies with the modified FITEXY routine. } 
follow $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
whereas late-type galaxies follow a shallower $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$ sequence.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{mag_vs_n_maj.pdf}
\caption{Spheroid absolute magnitude (at $3.6\rm~\mu m$) plotted against spheroid S\'ersic index 
measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend).
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:magn}
\end{center}
\end{figure}

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevented us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations. 
%($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
%and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we know that the early-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{1.03 \pm 0.11}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
therefore we expect to find $M_{\rm BH} \propto n_{\rm sph}^{3.69 \pm 0.44}$; 
this prediction is in excellent agreement with the observed log-slope of $3.58 \pm 0.27$ obtained here. 
On the other hand, late-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{2.58 \pm 1.06}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$, 
from which one can predict $M_{\rm BH} \propto n_{\rm sph}^{3.72 \pm 2.03}$; 
this is consistent with the observed log-slope of $4.55 \pm 0.66$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a log-slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a log-slope of $4.12 \pm 1.07$ for the late-type galaxies. 
Regardless of the linear regression routine used, 
the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph} - 0.50 \bigr) . 
\end{equation*}
\\

We have seen that the early- and late-type galaxies in the $M_{\rm BH} - n_{\rm sph}$ diagram 
can be fit (together) with a single power-law, 
whereas they follow two different correlations in the $M_{\rm BH} - L_{\rm sph}$ diagram (\emph{Paper II}). 
We now want to compare the amount of intrinsic scatter in these two plots. 
In Table \ref{tab:intsc} we report the values of the intrinsic scatter 
in the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams 
for all, early- and late-type galaxies, 
obtained with the modified FITEXY routine and the Bayesian estimator {\tt linmix\_err}. 
When considering all galaxies, irrespective of their morphological type, 
the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is smaller than that of the $M_{\rm BH} - L_{\rm sph}$ relation. 
However, this is obviously not a fair comparison, 
because of the different nature of the $M_{\rm BH} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ correlations 
(single and double power-law, respectively). 
One can obtain more informative results by considering early- and late-type galaxies separately. 
For the early-type galaxies, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent\footnote{Looking 
at the results obtained with the modified FITEXY routine, 
the values of the intrinsic scatter are only marginally consistent with each other, 
but looking at the results obtained with the Bayesian estimator {\tt linmix\_err}, 
the values of the intrinsic scatter are fully consistent with each other. } 
with that of the $M_{\rm BH} - L_{\rm sph}$ relation (within their $1\sigma$ uncertainties). 
For the late-type galaxies, the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation is consistent with 
that of the $M_{\rm BH} - L_{\rm sph}$ relation, 
except for the inverse ($X|Y$) regression obtained with the modified FITEXY routine. \\
In passing, we note that the values of the intrinsic scatter of the $M_{\rm BH} - n_{\rm sph}$ relation 
are systematically smaller -- although consistent within the errors -- 
than the corresponding values of the intrinsic scatter of the $M_{\rm BH} - L_{\rm sph}$ relation.  
In addition, the values of the intrinsic scatter returned by the modified FITEXY routine are systematically smaller than 
those output by the Bayesian estimator {\tt linmix\_err}.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{mbh_vs_n_maj.pdf}
\caption{Black hole mass plotted against spheroid S\'ersic index measured along the galaxy major-axis. 
Symbols are coded according to the galaxy morphological type (see legend). 
The orange crosses denote two lenticular galaxies (NGC 0524 and NGC 3998) which were excluded from the linear regression analysis 
(see Section \ref{sec:anal}). 
The red dashed line indicates the FITEXY bisector linear regression for the $45-2=43$  early-type galaxies (E+S0), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The shallower blue solid line shows the FITEXY bisector linear regression for the bulges of the 17 late-type (Sp) galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. 
The linear regressions for early- and late-type galaxies are consistent with each other within their $1\sigma$ uncertainties.  
The inset panel shows the error bars associated to each data point,  
where the error bars have the same color coding as the symbols in the main figure. 
}
\label{fig:mbhn}
\end{center}
\end{figure}
